Wide--Field Effects in Redshifted 21~cm Power Spectra

### 2015-03-11 ms.tex
Add preliminary section 3 "MWA Observations"
From b8d7b84:
============

In ms.tex,

(*) Add preliminary section 3 "MWA Observations"

>>>>

The MWA observations and data analysis used in this study are already described in \citet{thy15}. In order to reduce thermal fluctuations while maintaining coherence, it is essential to average independent data sets obtained over the same region of sky with identical beamformer settings. Hence, we select a subset of MWA snapshots each of duration 112~seconds obtained over different nights which are aligned to within 72~seconds of each other in {\it local sidereal time} (LST) around a mean LST of 0.04~hours with the MWA tile beam pointed at zenith. The database contains 14 snapshots satisfying these criteria. Two of these snapshots were found to contain amplitude and phase artifacts for a significant duration across different baselines. Hence, they have been excluded from our analysis.

The delay spectra of the rest of the snapshots were verified to be coherent in their amplitudes and phases. These complex valued delay spectra from independent snapshots are averaged together to lower thermal fluctuations without losing coherence from foreground contributions. The results are discussed below.
